Object-oriented implementations of the MPDATA advection equation solver in~C++,~Python~and~Fortran

### 2013-03-21 paper/doc/paper.tex
corecting Davide's surname spelling

    \noindent
    Tobias Burnus, Julian Cummings, Ond\v{r}ej \v{C}ert\'ik, Patrik Jonsson,
      Arjen Markus, Zbigniew Piotrowski, Davide del Vento and Janus Weil 
      provided valuable feedback to the initial version of the
      manuscript and/or responses to questions posted to Blitz++ and gfortran mailing lists.

>>>>

    \noindent
    Tobias Burnus, Julian Cummings, Ond\v{r}ej \v{C}ert\'ik, Patrik Jonsson,
      Arjen Markus, Zbigniew Piotrowski, Davide Del Vento and Janus Weil 
      provided valuable feedback to the initial version of the
      manuscript and/or responses to questions posted to Blitz++ and gfortran mailing lists.
